---
title: "Replication package"
output:
  github_document:
    toc: true
    toc_depth: 4
---

[![GitHub version](https://badge.fury.io/gh/gerasy1987%2Freplicate.svg)](https://badge.fury.io/gh/gerasy1987%2Freplicate)
[![Build Status](https://travis-ci.org/gerasy1987/replicate.svg?branch=master)](https://travis-ci.org/gerasy1987/replicate)
[![Coverage Status](https://coveralls.io/repos/github/gerasy1987/replicate/badge.svg?branch=master)](https://coveralls.io/github/gerasy1987/replicate?branch=master)

## TODO

- [ ] Discuss
- [x] ~~Transform into package~~
- [ ] Finish writing the ```summary.replication()``` method:
    - [x] ~~Add replication script functionality~~
    - [ ] Add description functionality for data, etc. (?)
- [ ] Implement ```output_table()``` functionality
- [ ] Test on Benin study (?)

## Description of the replicate functionality:

```{r global_options, echo=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, error=FALSE, eval = FALSE, echo = TRUE)
```

### ```create_replication()```

_The function takes main parts of replication object as an arguments and returns the replication class object. (see [create\_replication.R](https://github.com/gerasy1987/replicate/blob/master/create_replication.R) for code)._

The function takes 6 main arguments arguments (defaults are given in parentheses if specified):
  
  - ```description_list```: List of miscellaneous descriptions of replication. *Example*:
```{r example_1}
description_list =
  list(
    study_name = "Fake Study",
    study_authors = c("Georgiy Syunyaev", "Someone Else"),
    study_affiliations = c("Columbia University",
                           "Some Other University"),
    rep_authors = c("Georgiy Syunyaev"),
    study_abstract =
      paste0("The aim of this study is to test the create_replication() functionality. ",
             "This is the first attempt at creatreplication class of objects in [R] ",
             "for systematic storage and access to study replication materials.")
  )
```
    
  - ```packages``` (`= NULL`): Character vector of packages required for replication in `[R]`.
  - ```project_path``` (`= NULL`): Character string giving the path to the directory, where function and replication scripts are stored. Defaults to `NULL`, which is reasonable if RStudio project is used.
  - ```data_list```: A named list of data-frames used for the replication. *Example*:
    
```{r example_2}
data_list = list(data_admin = data_admin, data_individual = data_individual)
```
    
  - ```function_script_path```: Character string giving the name of `[R]` script which contains all functions required for the replication. The script should only include declarations of named functions using `<-` operator. See [replication\_functions.R](https://github.com/gerasy1987/replicate/blob/master/example/replication_functions.R) for example.
  - ```replication_script_path```: Character string giving the name of `[R]` script which contains all calls for table replications. The script should consist of only single calls for replication of one table and the table objects should be created using `<-` operator. See [replication\_script.R](https://github.com/gerasy1987/replicate/blob/master/example/replication_script.R) for example.
    
There are also 2 additional arguments:
  
  - ```quietly``` (```= FALSE```): Logical. Whether the creation of replication should go without any messages printed to `console`.
  - ```checks``` (```= TRUE```): Logical. If ```quietly = FALSE```, whether the checks for packages and consistency of replication should be performed.

### ```summary()```

_The function takes replication object and either returns miscellaneous description of the object, or if additional arguments are specified, then only summary of parts of object are returned. (see [summary.R](https://github.com/gerasy1987/replicate/blob/master/summary.R) for code)._

The function takes the following arguments:
  
  - ```object```: Object of class ```replication``` created by ```create_replication()```.
  - ```table``` (```= NULL```): Character string specifying the table to be replicated. The table name should include number of the table as specified in `replication_script_path` file and the word "table".
  - ```published``` (```= FALSE```): Logical. Whether to show columns with specifications published in the paper.
  - ```registered``` (```= FALSE```): Logical. Whether to show columns with specifications registered in PAP.
  - ```script``` (```= FALSE```): Logical. Whether to print the script to replicate the results of the study. If ```table = NULL```, then returns preamble which includes all the functions and packages required for replication. If ```table != NULL```, then returns preamble and the code for replication of the specified table.
  - ```desc``` (```= FALSE```): *To be implemented...*

### Examples

```{r setup, eval = TRUE}
devtools::install_github("gerasy1987/replication", quiet = TRUE)

library(replication)

load(file = "example/replication_data.Rdata")
```

#### Use of ```create_replication()```
```{r example_creation, eval=TRUE}

(
  x <-
  create_replication(
    data_list =
      list(data_admin = data_admin,
           data_individual = data_individual),
    packages =
      c("plyr", "dplyr", "broom", "Hmisc",
        "lfe", "multiwayvcov", "lmtest",
        "wakefield", "magrittr"),
    project_path = "example/",
    function_script_path = "replication_functions.R",
    replication_script_path = "replication_script.R",
    description_list =
      list(study_name = "Fake Study",
           study_authors = c("Georgiy Syunyaev", "Someone Else"),
           study_affiliations = c("Columbia University",
                                  "Some Other University"),
           rep_authors = c("Georgiy Syunyaev"),
           study_abstract = 
             paste0("The aim of this study is to test the create_replication() functionality. ",
                    "This is the first attempt at creatreplication class of objects in [R] ",
                    "for systematic storage and access to study replication materials.")),
    quietly = TRUE,
    checks = TRUE
  )
)
```

#### Use of ```summary.replication()```

1. Genearal summary

```{r general_summary, eval=TRUE, results='markup', collapse=FALSE, comment=""}
summary(x)
```

2. Table summary

```{r table_summary, eval=TRUE, results='markup', collapse=FALSE, comment=""}
summary(x, table = "table_1", published = TRUE, registered = FALSE)
summary(x, table = "table_2", published = TRUE, registered = TRUE)
```

3. Replication script

```{r replication_script, eval=TRUE, results='markup', collapse=FALSE, comment=""}
summary(x, script = TRUE)
summary(x, table = "table_1", script = TRUE)
```

#### Showcase for pre-existing replication object

1. Download the archive

```{r download_archive, eval=TRUE, results='markup', collapse=FALSE, comment=""}
download.file("https://github.com/gerasy1987/replicate/blob/master/example/fake_study.rdata?raw=True","fake_study.rdata")
load("fake_study.rdata")
```

2. Summarize the archive

```{r examine_archive, eval=TRUE, results='markup', collapse=FALSE, comment=""}
# Overall summary of the study
summary(fake_study)

# Here are the published results for Table 1
summary(fake_study, table = "table_1", published = TRUE, registered = FALSE)

# Here are the results for Table 1 registered in PAP
summary(fake_study, table = "table_2", published = FALSE, registered = TRUE)

# Here are both registered and published results for Table 1
summary(fake_study, table = "table_2", published = TRUE, registered = TRUE)

# Here is the preamble code you have to run to replicate any of the results in the study
summary(fake_study, script = TRUE)

# Here is the script which will reproduce Table 1
# if you have replication object in your R environment
# (which you have to have to run any of the above commands)
summary(fake_study, table = "table_1", script = TRUE)
```
